---
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    # latex_engine: lualatex
date: "`r format(Sys.time(), '%B %d, %Y')`"
title: "Postsecondary and Workforce Readiness Reports"
subtitle: "Random District"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
# reference_docx: ./Footemp.docx
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(scales)
library(extrafont)
library(extrafontdb)
library(ggthemes)

psdata <- read_csv("K:\\Research and Policy\\projects\\hs_feedback_report\\Derived Data File\\Mock District Data 20170405.csv")

dist <- psdata %>%
    filter(districtno == 350) %>%
    mutate(pct_enroll = round(100 * enroll_bin/hsgrad, 1)) %>%
    mutate(pct_enroll_state = round(100 * enroll_state/hsgrad_state))

distname <- subset(dist, page == "4" & institution_level == "Four-year University")

comp1 <- distname$similar_district_1
comp2 <- distname$similar_district_2
comp3 <- distname$similar_district_3
comp4 <- distname$similar_district_4
comp5 <- distname$similar_district_5
districtname <- "Random District"

```

# Cover page

# `r districtname`
## List of School Names
*************************

This page will contain a series of figures that in a clean way display for the most recent cohort. It will act as an introduction for the lay viewer. What are the key pieces of data that the state is monitoring and how does your school/district perform. 

*   Percent of most recent graduates who enrolled in any postsecondary institution
*   Percent of most recent graduates who enrolled in any postsecondary institution, by type of PS institution
*   Percent of most recent graduates concentrating in CTE
*   ~~Industry Certification Data~~
*   Average ACT scores 
<!-- *   Regional Alignment of Program of Studies available -->

## Overview of what we want to show.

This page would act as an introduction to the file.  

Some possible examples of what could be included would be:  

*   brief description of the data fields
*   Example figure to describe common themes/how to read figure
*   Definitions of key terms 
    +   Graduates, Seamless Enrollment, Cohort Year, EPSO, etc.
*   Introduction to Similar Districts concept and list Similar LEAs.

### Definitions  

**Freshman cohort**: a group of students who entered high school as freshmen in the same year. For example, this report provides data on the 2011 freshman cohort, which is a group of students who entered high school in the fall of 2011. The vast majority of these students graduated in the spring of 2015. This report uses freshman cohorts to emphasize the progress of a specific group of students.  

**Postsecondary Enrollment**: A student is identified as having enrolled in a postsecondary institution if they enroll within 12 months of expectred graduation year for students in the 2011 ninth grade cohort. Eligible institutions include Tennessee Board of Regents' schools, UT System, Tennessee Colleges of Applied Technology, TICUA institutions, and any non-Tennessee institution that shares enrollment information with the National Student Clearinghouse. 

**Postsecondary Remediation**: A student is identified as being assigned to a remedial course if they are designated as having non-zero remedial hours by their postsecondary institution. This information is only available from Tennessee public postsecondary institutions. At this time, the data are not able to be disaggregated at the subject level (e.g. we are unable to see whether a student took a remedial course in English or Math).

**Postsecondary Completion**: Postsecondary completion documentation is shown for students in the 2007 and 2008 ninth grade graduating cohorts, the earliest group of students that the Tennessee Longitudinal Data System can track from secondary into postsecondary. Any degree-granting public institution that submits completion information to THEC is included in this set of data points. For students in the 2007 ninth grade cohort, we display a 5 year completion rate and for students in the 2008 ninth grade cohort, we show a 4 year completion rate. As of "`r format(Sys.time(), '%B %d, %Y')`", the most recent term with completion information available is Summer 2016. A student's most advanced degree is shown. 

### District comparisons  
For some topics, comparing a school district's data to statewide trends is not illuminating because the characteristics of the district's student population are very different from the characteristics of the student population across Tennessee. For ACT and postsecondary enrollment data, this report provides comparisons to Tennessee school districts whose populations share similar demographic characteristics. Be respectful in your use of other school districts' information; do not share this information publicly.

|Your District | Comparison 1 | Comparison 2 | Comparison 3 | Comparison 4 | Comparison 5 |
|:-------------|:---------:|:---------:|:---------:|:---------:|:---------:|
|`r districtname`| `r comp1` | `r comp2` | `r comp3` | `r comp4` | `r comp5` |

**Notice**: These data are intended for use only by district personnel. Do not share these data outside of your district without written permission from the Tennessee Department of Education.  

\newpage

#### Key questions

*   What are the general enrollment trends in my district?
 
```{r Figure 3a, fig.height = 4, fig.width = 6, fig.align = 'center'}
dist %>%
    filter(page == "3a") %>%
    ggplot(aes(x = as.factor(cohortyear), y = pct_enroll, fill = as.factor(cohortyear))) +
        geom_bar(stat = "identity", position = position_dodge(), width = .75) +
        geom_text(aes(label = pct_enroll), vjust = -1) +
        theme_hc() +
        theme(axis.text.y = element_text(size=rel(1.25), family = "serif"),
            axis.text.x = element_text(size=rel(1.5), family = "serif", face = "bold"),
            plot.title = element_text(size=rel(1.5), family = "serif")) +
        scale_fill_manual(name = "Cohort Year", values = c("#e02f11", "#24336b", "#959595")) +
        ylab("Percent of graduates who enrolled \n in any postsecondary institution") +
        xlab("Graduating Cohort Year") +
        ggtitle("Postsecondary Enrollment by Cohort Year") +
        ylim(0, 100)
```

*   What type of institutions are my students enrolling in?

*   Percent of graduates who enrolled, by type of institution 
```{r Figure 3b, fig.height = 4, fig.width = 6, fig.align = 'center'}
dist %>%
    filter(page == "3b" & !is.na(institution_level)) %>%
    mutate(ps_pct_enroll = round(100 * enroll_bin/hsgrad_denom, 1)) %>%
    ggplot(aes(x = institution_level, y = ps_pct_enroll, fill = institution_level)) + 
        geom_bar(stat = "identity", position = "stack", width = .75) +
        geom_text(aes(label = ps_pct_enroll), vjust = -1) +
        theme_hc() +
        theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
            axis.text.x = element_text(size = rel(1.25), family = "serif", face = "bold"),
            plot.title = element_text(size = rel(1.5), family = "serif")) +
        scale_fill_manual(name = "Institution Level", values = c("#e02f11", "#24336b", "#959595")) + 
        ylab("Percent of high school graduates who enrolled in \n postsecondary institution") +
        xlab("Institution Level") +
        ggtitle("Postsecondary Enrollment by Institution Type \n 2015 On-time Graduates") +
        ylim(0, 100)
```

*   How does enrollment differ across schools in my district?

```{r Figure3c, fig.height = 5, fig.width = 8}
dist %>%
    filter(page == "3c" & !is.na(institution_level)) %>%
    mutate(ps_pct_enroll = round(100 * (enroll_bin / hsgrad_denom), 1),
           p3c_label = paste(institution_level, " (", ps_pct_enroll, "%)", sep = "")) %>%
    ggplot(aes(x = institution_level, y = ps_pct_enroll, fill = institution_level)) +
        geom_bar(stat = "identity", colour = "black", show.legend = FALSE) +
        geom_text(aes(label = ps_pct_enroll), vjust = -1, position = "stack") +
        theme_hc() +
        theme(axis.text.y = element_text( family = "serif"),
            axis.text.x = element_text(hjust = .75, angle = 15, family = "serif", face = "bold"),
            plot.title = element_text(family = "serif")) +
        facet_grid(. ~ schoolname) +
        scale_fill_manual(name = "Institution Level", values = c("#e02f11", "#24336b", "#959595")) +
        ylab("Percent of graduates who enrolled \n in any postsecondary institution") +
        xlab("Institution Type") +
        ggtitle("Postsecondary Enrollment by High School 2015 On-time Graduates") +
        ylim(0,100)
```

\newpage

We hope to show more data with comparisons to similar districts.  

#### Key Questions
*   How does my school compare to similar districts in terms of postsecondary enrollment? Higher? Lower? 
```{r , echo=FALSE}

district_order <- dist %>%
    filter(page == "4" & institution_level == "Four-year University") %>%
    select(districtname, similar_district_1, similar_district_2, similar_district_3, similar_district_4, similar_district_5) %>%
    t() %>%
    as_data_frame() %>% 
    magrittr::extract2(1) %>% 
    c("State")

master <- dist %>%
    filter(page == "4") %>%
    transmute(institution_level, `Similar District` = districtname, pct_enroll)

similar_1 <- dist %>%
    filter(page == "4") %>%
    transmute(institution_level, `Similar District` = similar_district_1, pct_enroll = round(100 * enroll_bin1/hsgrad_denom1, 1))

similar_2 <- dist %>%
    filter(page == "4") %>%
    transmute(institution_level, `Similar District` = similar_district_2, pct_enroll = round(100 * enroll_bin2/hsgrad_denom2, 1))

similar_3 <- dist %>%
    filter(page == "4") %>%
    transmute(institution_level, `Similar District` = similar_district_3, pct_enroll = round(100 * enroll_bin3/hsgrad_denom3, 1))

if (length(na.omit(dist$similar_district_4)) != 0) {
    similar_4 <- dist %>%
        filter(page == "4") %>%
        transmute(institution_level, `Similar District` = similar_district_4, pct_enroll = round(100 * enroll_bin4/hsgrad_denom4, 1))
}

if (length(na.omit(dist$similar_district_5)) != 0) {
    similar_5 <- dist %>%
        filter(page == "4") %>%
        transmute(institution_level, `Similar District` = similar_district_5, pct_enroll = round(100 * 
            as.numeric(enroll_bin5)/as.numeric(hsgrad_denom5), 1))
}

state <- dist %>%
    filter(page == "4") %>%
    transmute(institution_level, `Similar District` = "State", pct_enroll = pct_enroll_state)

if (exists("similar_4") & exists("similar_5")) {
    all_districts <- bind_rows(master, similar_1, similar_2, similar_3, similar_4, similar_5, state) %>%
        spread(institution_level, pct_enroll)
}

if (exists("similar_4") & !exists("similar_5")) {
    all_districts <- bind_rows(master, similar_1, similar_2, similar_3, similar_4,  state) %>%
        spread(institution_level, pct_enroll)
}

if (!exists("similar_4") & !exists("similar_5")) {
    all_districts <- bind_rows(master, similar_1, similar_2, similar_3, similar_4,  state) %>%
        spread(institution_level, pct_enroll)
}

all_districts[match(district_order, all_districts$`Similar District`), ] %>%
    knitr::kable()

all_districts %>%
    gather(institution_level, `Percent Enrolled`, -`Similar District`) %>%
    ggplot(aes(x = `Similar District`, y = `Percent Enrolled`, fill = institution_level)) +
        geom_bar(stat = "identity", colour = "black", show.legend = FALSE) +
        geom_text(aes(label = `Percent Enrolled`), vjust = 1, position = "stack") +
        theme_hc() +
        theme(axis.text.x = element_text(hjust = .75,size = rel(1.2), angle = 15, family = "serif")) +
        scale_fill_manual(name = "Institution Level", values = c("#e02f11", "#24336b", "#959595")) +
        scale_x_discrete(limits = district_order) +
        ylim(0, 100)
```

**Comparison notes**: In our meeting on 2/15, we decided that we would have a comparison district data shown for comp LEAs rather than an aggregation at the district level. (if we choose to do schools): At the school level, we would do a comparison to other schools within your district if more than 2 schools. If 2 or fewer, they would be compared to comparison LEAs' aggregated data. As of "`r format(Sys.time(), '%B %d, %Y')`", I have not coded this difference into the report generating process. Below is a table of the number of LEAs who operate the given number of schools.

#### Number of Schools in Each District

|Number of Schools in LEA| Number of LEAs|
|:-----|:-----:|
|1|	69|
|2	|25|
|3|	13|
|4|	10|
|5|	2|
|6|	1|
|7|	1|
|8|	1|
|9|	2|
|10|	1|
|15|	1|
|21|	1|
|26|	1|
|44|	1|

\newpage

## Postsecondary Enrollment by Subgroup (Most recent year only)

#### Key Questions
*    Racial demographics (State Comparison, District, and school level)
    +   To what extent do we see equitable access by race within the district to postsecondary institutions? Given this information, do you feel that all students are receiving the same opportunities in your district?

```{r Figure5a, fig.height = 6, fig.width = 8}
dist %>%
    filter(page == "5a" & hsgrad_denom >= 10 & !is.na(institution_level)) %>%
    ggplot(aes(x = as.factor(race), y = pct_enroll, fill = institution_level)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = pct_enroll), vjust = 2, position = "stack") +
    theme_hc() +
    theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
          axis.text.x = element_text(size = rel(1.5), family = "serif", face = "bold"),
          plot.title = element_text(size = rel(1.5), family = "serif")) +
    facet_grid(. ~ schoolname)  +
    scale_fill_manual(name = "Institution Level", values = c("#e02f11", "#24336b", "#959595")) +
    ylab("Percent of graduates who enrolled \n in any postsecondary institution in 2015") +
    xlab("Racial/Ethnic Group by School") +
    ggtitle("Postsecondary Enrollment by Subgroup") +
    ylim(0, 100)
```

*    Economic Disadvantage (School level)  
    +   To what extent do we see equitable access by level of economic disadvantage in my district to postsecondary institutions? Given this information, do you feel that all students are receiving the same opportunities in your district?
    
```{r Figure5c, fig.height = 6, fig.width = 8}
dist %>%
    filter(page == "5c" & hsgrad_denom >= 10 & !is.na(institution_level)) %>%
    ggplot(aes(x = econ_dis, y = pct_enroll, fill = as.factor(institution_level))) + 
        geom_bar(stat = "identity") +
        geom_text(aes(label = pct_enroll), vjust = 1, position = "stack") +
        theme_hc() +
        theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
            axis.text.x = element_text(size = rel(1.5), family = "serif", face = "bold"),
            plot.title = element_text(size = rel(1.5), family = "serif")) +
        facet_grid(. ~ schoolname) +
        scale_fill_manual(name = "Institution Level", values = c("#e02f11", "#24336b", "#959595")) +
        ylab("Percent of graduates who enrolled \n in any postsecondary institution in 2015") +
        xlab("Economic Disadvantage Status by School") +
        ggtitle("Postsecondary Enrollment by Subgroup") +
        ylim(0, 100)
```

\newpage

## Postsecondary Enrollment By Academic Achievement (Most recent year only)

#### Key Questions

*   Consider the distribution of ACT composite scores for the students in your district. 
```{r Figure7aa, fig.height = 6, fig.width = 8}
dist %>%
    filter(page == "7a") %>%
    group_by(districtno, districtname, schoolname, schoolno, act_recode) %>% 
    summarise(`Number at ACT score`= max(hsgrad_denom)) %>% 
    group_by(schoolno) %>%
    mutate(`Number Grads` = sum(`Number at ACT score`),
        `Percent at ACT score` = round(100 * `Number at ACT score`/`Number Grads`, 1)) %>% 
    select(districtname, districtno, schoolno, schoolname, act_recode,
        `Percent at ACT score`, `Number at ACT score`, `Number Grads`) %>% 
    ggplot(aes(x = act_recode, y = `Percent at ACT score`, fill = act_recode)) + 
        geom_bar(stat = "identity") +
        geom_text(aes(label = `Percent at ACT score`), vjust = -1, position = "stack") +
        theme_hc() +
        theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
            axis.text.x = element_text(size = rel(1.5), family = "serif", hjust = .5, angle = 15),
            plot.title = element_text(size = rel(1.5), family = "serif")) +
        facet_grid(. ~ schoolname) +
        scale_fill_manual(name = "ACT Composite Score", values = c("#2dccd3", "#5d7975", "#e02f11", "#24336b", "#959595")) +
        ylab("Percent of graduates who scored at \n at different ACT score bands in 2015") +
        xlab("Students' Highest ACT Composite Score") +
        ggtitle("Distribution of ACT Composite Scores") +
        ylim(0, 100)
```

*   Overall Enrollment By ACT Scores (State Comparison, District, and school level)
The above figure displays the distribution of ACT scores. That group of students becomes the denominator for the next figure that shows postsecondary enrollment rates at each ACT score band. Thus, if a school had 50 students score between a 19-20, and 40 of those students enrolled in a postsecondary institution, the overall enrollment for that score band would be 80%. 
    +   To what extent do ACT Scores relate to the postsecondary enrollment of the students in my district? 

```{r Figure7a, fig.height = 6, fig.width = 8}
dist %>%
    filter(page == "7a" & hsgrad_denom >= 5 & !is.na(institution_level)) %>%
    ggplot(aes(x = act_recode, y = pct_enroll, fill = as.factor(institution_level))) + 
    geom_bar(stat = "identity") +
    geom_text(aes(label = pct_enroll), vjust = 1, position = "stack") +
    theme_hc() +
    theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
          axis.text.x = element_text(size = rel(1.5), family = "serif", hjust = .5, angle = 15),
          plot.title = element_text(size = rel(1.5), family = "serif")) +
    facet_grid(. ~ schoolname) +
    scale_fill_manual(name = "Institution Level", values = c("#e02f11", "#24336b", "#959595")) +
    ylab("Percent of graduates who enrolled \n in any postsecondary institution in 2015") +
    xlab("Students' Highest ACT Composite Score") +
    ggtitle("Postsecondary Enrollment by ACT Score") +
    ylim(0, 100)
```
    
* Other possible questions    
    +   To what extent does the relationship between ACT scores and postsecondary enrollment in your district differ from the state average?
    +   To what extent does the relationship between ACT scores and the type of postsecondary institution where students are enrolling in your district differ from the state average?
    
\newpage

## Postsecondary Enrollment By Coursework  (Most recent year only)

#### Key questions
*   To what extent do all students have access to rigorous coursework that can result in early postsecondary credit in the 2011 graduating cohort who graduated in spring 2015? 

```{r Figure9a, fig.height = 6, fig.width = 8}

epso <- dist %>%
    filter(page == "9a") %>%
    group_by(districtno, districtname, schoolname, schoolno) %>% 
    summarise(`Number who took EPSO`= max(epso_new), `Number Grads` = sum(hsgrad_denom)) %>%
    ungroup() %>%
    transmute(districtname, districtno, schoolno, schoolname, 
        Percent = `Number who took EPSO` / `Number Grads`, `EPSO type` = "Any EPS")
    
AP <- dist %>%
    filter(page == "9a") %>%
    group_by(districtno, districtname, schoolname, schoolno) %>% 
    summarise(`Number who took AP`= max(ap_stu), `Number Grads` = sum(hsgrad_denom)) %>%
    ungroup() %>%
    transmute(districtname, districtno, schoolno, schoolname, 
        `Percent` = `Number who took AP` / `Number Grads`, `EPSO type` = "AP Course")

DE <- dist %>%
    filter(page == "9a") %>%
    group_by(districtno, districtname, schoolname, schoolno) %>%
    summarise(`Number who took Dual Enrollment`= max(de_ever), `Number Grads` = sum(hsgrad_denom)) %>%
    ungroup() %>%
    transmute(districtname, districtno, schoolno, schoolname,
        Percent = `Number who took Dual Enrollment` / `Number Grads`, `EPSO type` = "DE Course")
    
EPS_ANY <- bind_rows(epso, AP, DE)
    
EPS_ANY %>%
    mutate(Percent = round(100 * Percent,1)) %>%
    ggplot(aes(x = `EPSO type`, y = Percent, fill = `EPSO type`)) +
        geom_bar(stat = "identity") +
        geom_text(aes(label = Percent), vjust = -1, position = "stack") +
        theme_hc() +
        theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
            axis.text.x = element_text(size = rel(1.5), family = "serif", hjust = .5, angle = 15),
            plot.title = element_text(size = rel(1.5), family = "serif")) +
        facet_grid(. ~ schoolname) +
        scale_fill_manual(name = "EPS course taking", values = c("#e02f11", "#24336b", "#959595")) +
        ylab("Percent of graduates who participated in EPS courses \n in 2015") +
        xlab("EPS course taken") +
        ggtitle("Percent of Grads who took Early Postsecondary Course") +
        ylim(0, 100)
```

*   To what extent does access to EPS courses differ by student race?

```{r Figure9b, fig.height = 6, fig.width = 8}

epso1 <- dist %>%
    filter(page == "9b" & hsgrad >= 10) %>% 
    transmute(districtname, districtno, schoolno, schoolname, race,
        Percent = epso_new/hsgrad, `EPSO type` = "Any EPS")
  
AP1 <- dist %>%
    filter(page == "9b" & hsgrad >= 10) %>%
    transmute(districtname, districtno, schoolno, schoolname, race,
        Percent = ap_stu/hsgrad, `EPSO type` = "AP Course")

DE1<- dist %>%
    filter(page == "9b" & hsgrad >= 10) %>%
     transmute(districtname, districtno, schoolno, schoolname, race,
        Percent = de_ever/hsgrad, `EPSO type` = "DE Course", `Number Grads` = hsgrad)
    
EPS_ANY1 <- bind_rows(epso1, AP1, DE1)
    
EPS_ANY1 %>% 
    mutate(Percent = round(100 * Percent, 1)) %>% 
    ggplot(aes(x = race, y = Percent, fill = `EPSO type`)) +
        geom_bar(stat = "identity", position = "dodge") +
        geom_text(aes(label = Percent),  position = position_dodge(0.9), vjust = -1) +
        theme_hc() +
        theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
            axis.text.x = element_text(size = rel(1.5), family = "serif", hjust = .5, angle = 15),
            plot.title = element_text(size = rel(1.5), family = "serif")) +
        facet_grid(. ~ schoolname) +
        scale_fill_manual(name = "EPS course taking", values = c("#e02f11", "#24336b", "#959595")) +
        ylab("Percent of graduates who participated \n in EPS courses in 2015") +
        xlab("Race") +
        ggtitle("Percent of Grads who took Early Postsecondary Course") +
        ylim(0, 100)
```

*   To what extent does this differ by the economic disadvantage status of the students? 

```{r Figure9c, fig.height = 6, fig.width = 8}

epso2 <- dist %>%
    filter(page == "9c" & hsgrad >= 10) %>%
    transmute(districtname, districtno, schoolno, schoolname, econ_dis, 
        Percent = epso_new/hsgrad, `EPSO type` = "Any EPS")
  
AP2 <- dist %>%
    filter(page == "9c" & hsgrad >= 10) %>%
    transmute(districtname, districtno, schoolno, schoolname, econ_dis,
        Percent = ap_stu/hsgrad, `EPSO type` = "AP Course")
    
DE2 <- dist %>%
    filter(page == "9c" & hsgrad >= 10) %>%
    transmute(districtname, districtno, schoolno, schoolname, econ_dis,
        Percent = de_ever/hsgrad, `EPSO type` = "DE Course", `Number Grads` = hsgrad)
    
EPS_ANY2 <- bind_rows(epso2, AP2, DE2)
    
EPS_ANY2 %>% 
    mutate(Percent = round(100 * Percent, 1),
    ED = ifelse(econ_dis == "Y","Econ. Dis.", "Not Econ. Dis.")) %>% 
    ggplot(aes(x = ED, y = Percent, fill = `EPSO type`)) +
        geom_bar(stat = "identity", position="dodge") +
        geom_text(aes(label = Percent),  position = position_dodge(0.9), vjust = -1) +
        theme_hc() +
        theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
            axis.text.x = element_text(size = rel(1.5), family = "serif", hjust = .5, angle = 15),
            plot.title = element_text(size = rel(1.5), family = "serif")) +
        facet_grid(. ~ schoolname) +
        scale_fill_manual(name = "EPS course taking", values = c("#e02f11", "#24336b", "#959595")) +
        ylab("Percent of graduates who participated \n in EPS courses in 2015") +
        xlab("Economic Disadvantage Status") +
        ggtitle("Percent of Grads who took Early Postsecondary Course") +
        ylim(0, 100)
```    

*   To what extent do students who took EPS courses enroll in a postsecondary institution?
*   To what extent do students who took EPS courses enroll in different types of postsecondary institutions?

```{r Figure9d, fig.height = 5, fig.width = 8}
dist %>%
    filter(page == "9d") %>%
    group_by(schoolno, epso_new) %>%
    mutate(`Number Grads` = sum(hsgrad)) %>%
    filter(`Number Grads` >= 10 & !is.na(institution_level)) %>%
    ungroup() %>%
    mutate(EPS_cat = ifelse(epso_new == 1, "EPS", "No EPS"),
        `Percent Enroll` = round(100 * enroll_bin / `Number Grads`, 1)) %>%
    select(districtname, districtno, schoolno, schoolname, institution_level, EPS_cat, `Percent Enroll`, `Number Grads`) %>%
    ggplot(aes(x = EPS_cat, y = `Percent Enroll`, fill = institution_level)) +
        geom_bar(stat = "identity") +
        geom_text(aes(label = `Percent Enroll`), vjust = 1, position = "stack") +
        theme_hc() +
        theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
            axis.text.x = element_text(size = rel(1.5), family = "serif", hjust = .5, angle = 15),
            plot.title = element_text(size = rel(1.5), family = "serif")) +
        facet_grid(. ~ schoolname) +
        scale_fill_manual(name = "Institution level", values = c("#e02f11", "#24336b", "#959595")) +
        ylab("Percent of graduates who enrolled in a \n PS institution by EPS in 2015") +
        xlab("Whether Student took EPS course") +
        ggtitle("Postsecondary Enrollment by EPS coursetaking") +
        ylim(0, 100)
```

Research by the department has seen increases in postsecondary enrollment for ED students who take early postsecondary courses. 

* To what extent do Economically Disadvantaged students benefit from EPS courses?

```{r Figure9e, fig.height = 5, fig.width = 8}
dist %>%
    filter(page == "9e") %>%
    group_by(schoolno, epso_frpl_cat) %>% 
    mutate(`Number Grads` = sum(hsgrad)) %>% 
    filter(`Number Grads` >= 10 & !is.na(institution_level)) %>% 
    ungroup() %>% 
    mutate(`Percent Enroll` = round(100 * enroll_bin / `Number Grads`, 1)) %>% 
    select(districtname,districtno, schoolno, schoolname, institution_level, epso_frpl_cat, `Percent Enroll`, `Number Grads`) %>% 
    ggplot(aes(x = epso_frpl_cat, y = `Percent Enroll`, fill = institution_level)) + 
        geom_bar(stat = "identity") +
        geom_text(aes(label = `Percent Enroll`), vjust = 1, position = "stack") +
        theme_hc() +
        theme(axis.text.y = element_text(size = rel(1.25), family = "serif"),
            axis.text.x = element_text(size = rel(1.5), family = "serif", hjust = .5, angle = 15),
            plot.title = element_text(size = rel(1.5), family = "serif")) +
        facet_grid(. ~ schoolname) +
        scale_fill_manual(name = "Institution level", values = c("#e02f11", "#24336b", "#959595")) +
        ylab("Percent of graduates who enrolled in a \n PS institution by EPS in 2015") +
        xlab("Whether Student took EPS course, \n by Economic Disadvantage status") +
        ggtitle("Postsecondary Enrollment by EPS coursetaking") +
        ylim(0,100)
```    

\newpage

## Most Common Institutions

*   Number of students who enrolled in each institution for 2011 cohort
    -    or for 3 most previous cohorts or by cohort? It's unclear to me what is more useful here: To have a broader picture or think about those specific students? What would move districts to consider the pathways onto which their students are embarking? 
    
```{r, echo = FALSE}
# Do I want to show this by school?
dist %>%
    filter(page == "8" & enroll_bin >= 5 & !is.na(institution_level)) %>%
    arrange(desc(enroll_bin)) %>%
    slice(1:10) %>%
    mutate(`Number of Enrollees` = enroll_bin, `Institution Name` = ps_institution_name) %>%
    select(`Institution Name`, `Number of Enrollees`) %>%
    knitr::kable()
```

\newpage

## Persistence of all students (Not included in initial release)
*   Earning 1 year worth of credits in two years
*   Remediation (by subject) 
  *   WILL BE INCLUDED IN INITITAL REPORT

## Completion Rates by Institution Type (5 year (2007 cohort), 4 year (2008 cohort))

\newpage

# Appendix A
# CTE Focused Section

For the next set of figures, we would focus on the same data that was provided at the school and district level, but focus at the concentrator level. We will compare across program areas where applicable. 

## Appendix B: Strategies??? 
CCTE Team would develop a series of strategies that would target potential stories that would arise from the data

## Appendix C: Business Rules/Data Sources: 

When we release data, we have to make sure that we clear set of business rules defined. 

# Preliminary timeline

### April 7 (CORE Data analysts in town)
We are looking to have a working session with the data analysts to get a full set of feedback: What questions would you want to ask? How would you approach X issue? Do these figures make sense? 

### April 20
Based on CORE feedback, we would put together the final mock-ups to share within the department, to THEC, TOSS, etc
Bring in communications team for state level communication plans

### Middle of May
To Directors with instructions to reach out to CORE Data analysts
Validation period

### June
Release of Reports